A Loop Quantm Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales

### 2025-07-02 AoP/response-to-referee.tex

\emph{This duality is reminiscent of, but also distinct from, the T and S dualities in string theory. In T-duality the behavior of a string compactified on a circle of radius $R$ is related to the behavior of a string compactified on a circle of radius $\alpha'/R$. In S-duality the physics at strong string coupling $g_s \gg 1$ can be mapped to the physics at weak string coupling $g_s \ll 1$. In our case, the duality is between a description of physics at large string tension $T$ and small worldsheet areas $h_{ab}$ and a description of physics at small string tension $T'$ and large worldsheet areas $h'_{ab} = (h_{ab})^{-1}$. This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence.}

\subsection{Section 3 - Part (a): Bimetric String and Ghost Avoidance}

\RC The author introduces the connection to bimetric gravity, but the analogy should be strengthened by discussing how the bimetric string avoids issues like the Boulware-Deser ghost.

\AR We had already mentioned the Boulware-Deser ghost avoidance in Section 2, right after the section when we talk about duality between the area metric and its inverse. As for how this would affect string theory, we feel that a proper discussion of this issue would be beyond the scope of this paper and would require a separate paper in its own right. We have added the following paragraph in Section 3 addressing this point, right after "Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''":

\emph{As mentioned at the end of the previous section, the appeal of bimetric gravity lies in the fact that it eliminates the Boulware-Deser ghost in theories of massive gravity. However, what effect this would have on stringy dynamics, beyond the ansatz for a bimetric string action we have given above, and which to our knowledge is the first time such an expression has been written down, is beyond the scope of the present work and would require a separate paper in its own right.}

@@

\subsection{Section 3 - Part (b): Kalb-Ramond Field Connection}

\RC The link between $\Delta_{ab}$ and the Kalb-Ramond field $B_{\mu\nu}$ (Sec. 3.2) is a highlight, but the derivation of Eq. (3.21) should be detailed for clarity.

\AR \AR The derivation of the relation between $\Delta_{ab}$ and the Kalb-Ramond field $B_{\mu\nu}$ is detailed in Section 4a, specifically in equations (4.12) and (4.13). Equation (4.12) shows the area-corrected string action coupled to the Kalb-Ramond field, while equation (4.13) demonstrates that by varying this action with respect to $\Delta^{cd}$, we obtain $\Delta_{cd} = \widetilde{f} \partial_c X^\mu \partial_d X^\nu B_{\mu\nu}$, establishing the explicit connection between the worldsheet quantum of area tensor and the pullback of the bulk Kalb-Ramond field.

@@

\subsection{Section 3 - Part (c): Bimetric Gravity Background}

\RC The section assumes familiarity with bimetric gravity, a brief review of key concepts would aid readers outside this niche.

\AR We agree that a comprehensive review of bimetric gravity would aid readers unfamiliar with this area. However, we feel that including such a review would take the paper too far afield from its main focus on the LQG-inspired string action. We have provided the key reference to seminal works \citep{de-Rham2011Resummation, Hassan2012Bimetric} for readers who wish to explore bimetric gravity in greater detail.

@@

\subsection{Section 4 - Part (a): Physical Meaning of Coupling}

\RC In equations (4.7-4.10) the physical meaning of the coupling between $\phi(x)$, $\Delta$ and $X^\mu$ (akin to a dilaton) needs a more thorough explanation.

\AR We have expanded the paragraph following eqn 4.10, from the following:

\emph{revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \citep{Balthazar-t-backgrounds}.}

to:

\emph{revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields. The coupling term $\frac{(2\partial_a \phi - \partial_a \ln(\Delta))}{\frac{2e^{2\phi}}{k\Delta} - 1}$ shows how the area quantization correction modifies the propagation of embedding coordinates - the numerator combines gradients from both conformal and quantum geometric effects, while the denominator represents the modification to the wave operator due to LQG's minimal area constraint. This behavior is much akin to the dilaton field \citep{Balthazar-t-backgrounds}.}

@@

\subsection{Section 4 - Part (b): Born-Infeld Analogy}

\RC The Born-Infeld analogy (Sec. 4.2) should address why the Kalb-Ramond field must be exact.

\AR The mention of exactness in the Born-Infeld analogy section is an additional observation rather than a requirement for the analogy itself. The core point is the structural similarity between our area-corrected action and the Born-Infeld form, where $\Delta _{ab}$ plays the role of a field strength. The exactness condition and its implications for background torsion, while potentially interesting, are not essential to this analogy and can be omitted without affecting the main argument. We have accordingly edited the paragraph following eqn 4.10 to omit the reference to exactness and torsion, from:

\emph{thus the action (2.2) can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{ab}$ the role of the pullback of a field strength. Since we explored the relation between $\Delta _{ab}$ and the Kalb-Ramond field $B_{\mu \nu}$ in Section 4A, this could mean that the Kalb-Ramond 2-form is exact, $B = d A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $d B = d (d A) = 0$. Also, we have a direct relation between string tension and scale ...}

to:

\emph{thus the action (2.2) can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{ab}$ the role of the pullback of a field strength. Also, we have a direct relation between string tension and scale ...}

### 2025-07-02 lqg-strings.tex
feat: T2 - complete sections 3-4 reviewer responses for AOP submission
- Add bimetric ghost limitation acknowledgment in manuscript
- Expand dilaton coupling explanation after eq 4.10
- Remove tangential exactness discussion from Born-Infeld section
- Complete all section 3-4 response document entries
- Ready for section 5 reviewer responses
- Updated memory bank

@@

The Nambu-Goto area-corrected action before approximations \eqref{eqn:ng-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
\begin{equation} \label{eqn:BI-action}
	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
\end{equation}
with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string. Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
\end{equation}
thus the action \eqref{eqn:ng-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength. Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$. Also, we have a direct relation between string tension and scale
\begin{equation} \label{eqn:k-T}
	\frac{l_{pl}}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
\end{equation}

>>>>

As mentioned at the end of the previous section, the appeal of bimetric gravity lies in the fact that it eliminates the Boulware-Deser ghost in theories of massive gravity. However, what effect this would have on stringy dynamics, beyond the ansatz for a bimetric string action we have given above, and which to our knowledge is the first time such an expression has been written down, is beyond the scope of the present work and would require a separate paper in its own right.

@@

The Nambu-Goto area-corrected action before approximations \eqref{eqn:ng-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
\begin{equation} \label{eqn:BI-action}
	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
\end{equation}
with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string. Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
\end{equation}
thus the action \eqref{eqn:ng-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength. Also, we have a direct relation between string tension and scale
\begin{equation} \label{eqn:k-T}
	\frac{l_{pl}}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
\end{equation}
